Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-07-10 patchy-selection-paper.tex
made sections non-numbered CORRECTLY now

@@

%%%
\subsection*{Model of a patchy landscape}
\label{ss:patchyspace}

@@

%%%%%%%
\subsection*{Simulation methods}
\label{ss:simulations}

@@

%%%% %%%%
\subsubsection*{The genealogy of migrant families}

@@

%%%%%%% %%%%%%%%%%%
\subsubsection*{The outflux of migrant alleles}

@@

%%%%%%%%%%%%
\subsubsection*{Multiple patches}
Above we worked with two patches separated by distance $R$;
but these calculations apply as well to multiple patches
in which the $B$ allele can facilitate local adaptation. 
Under our assumptions of selective exclusion and rapid establishment, 
each patch will adapt through establishment of a single copy of the $B$ allele, 
either by migration or mutation.
If we imagine that the times between successive establishments are the result of many nearly-independent attempts
with small probability of success,
the process of occupation is well approximated by a Markov chain,
whose state records the labeling of patches according to the colonizing allele
(or none, for those that haven't yet adapted).

@@

%%%%%%%%%%
\subsection*{Applications} 
\label{ss:applications}
% FOR REFERENCE:
% On Wed, May 28, 2014 at 10:20 AM, Michael Nachman <mnachman@berkeley.edu> wrote:
% > Graham:
% >
% > The density is probably in the range of 10-40 animals per hectare (10,000
% > m^s).  We built enclosures of 0.25 hectare and found that they could support
% > about 10 animals with food provided ad libitum, so I think this is an upper
% > density (i.e.\ 40/hectare).  As for dispersal distance, I'm less sure.
% > Studies on closely related species (genus Perognathus) in similar habitats
% > suggest distances of 100's of feet.  Attached are some old papers that tried
% > to estimate dispersal distances in Perognathus.
% > best,
% > Michael

@@

\subsection*[Probability of Establishment]{Numerical calculation of the probability of establishment}
\label{apx:establishment_sims}

@@

%%%%%%%%%%%%
\subsection*[Equilibrium Frequency]{The equilibrium frequency}
\label{apx:eqfreq}

@@

%%%%%%%%%%%
\subsection*[Asymptotics]{Asymptotic solution for the equilibrium frequency} 
\label{apx:asymptotics}

@@

%%%%%%%%% %%%%%%%%%%%%%%
\subsection*[Hitting and Occupation]{Hitting and occupation}
\label{apx:hitting_occupation}

@@

%%%%%%% %%%%%%%%%%%%
\subsection*[Outflux of Families]{The outflux of families}
\label{apx:outflux}

@@

>>>>

\setcounter{secnumdepth}{0}

@@

%%%
\subsection{Model of a patchy landscape}
\label{ss:patchyspace}

@@

%%%%%%%
\subsection{Simulation methods}
\label{ss:simulations}

@@

%%%% %%%%
\subsubsection{The genealogy of migrant families}

@@

%%%%%%% %%%%%%%%%%%
\subsubsection{The outflux of migrant alleles}

@@

%%%%%%%%%%%%
\subsubsection{Multiple patches}
Above we worked with two patches separated by distance $R$;
but these calculations apply as well to multiple patches
in which the $B$ allele can facilitate local adaptation. 
Under our assumptions of selective exclusion and rapid establishment, 
each patch will adapt through establishment of a single copy of the $B$ allele, 
either by migration or mutation.
If we imagine that the times between successive establishments are the result of many nearly-independent attempts
with small probability of success,
the process of occupation is well approximated by a Markov chain,
whose state records the labeling of patches according to the colonizing allele
(or none, for those that haven't yet adapted).

@@

%%%%%%%%%%
\subsection{Applications} 
\label{ss:applications}
% FOR REFERENCE:
% On Wed, May 28, 2014 at 10:20 AM, Michael Nachman <mnachman@berkeley.edu> wrote:
% > Graham:
% >
% > The density is probably in the range of 10-40 animals per hectare (10,000
% > m^s).  We built enclosures of 0.25 hectare and found that they could support
% > about 10 animals with food provided ad libitum, so I think this is an upper
% > density (i.e.\ 40/hectare).  As for dispersal distance, I'm less sure.
% > Studies on closely related species (genus Perognathus) in similar habitats
% > suggest distances of 100's of feet.  Attached are some old papers that tried
% > to estimate dispersal distances in Perognathus.
% > best,
% > Michael

@@

\subsection[Probability of Establishment]{Numerical calculation of the probability of establishment}
\label{apx:establishment_sims}

@@

%%%%%%%%%%%%
\subsection[Equilibrium Frequency]{The equilibrium frequency}
\label{apx:eqfreq}

@@

%%%%%%%%%%%
\subsection[Asymptotics]{Asymptotic solution for the equilibrium frequency} 
\label{apx:asymptotics}

@@

%%%%%%%%% %%%%%%%%%%%%%%
\subsection[Hitting and Occupation]{Hitting and occupation}
\label{apx:hitting_occupation}

@@

%%%%%%% %%%%%%%%%%%%
\subsection[Outflux of Families]{The outflux of families}
\label{apx:outflux}

@@

\setcounter{secnumdepth}{2}
